Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
Fixed section 3 lemma

This theorem is proven in three different genus cases, each of
which use similar inductive processes. The high genus case is
proven in Theorem ~\ref{thm:g-high-main}. In Theorem
~\ref{thm:g-1-main} and Theorem
~\ref{thm:g-0-main}, we also give the respective
genus one and genus zero results after using a similar induction
process while dealing with more complicated base cases and
exceptional cases.

@@

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
\end{enumerate}

\begin{rem}
\label{rem:delta-not-1}
Suppose $(\sx,\Delta,L)$ is a log spin curve. Note that $\deg \Delta
$ is even. because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K
\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
In particular, we shall often use $\deg \Delta \neq 1$.
\end{rem}

@@

\begin{rem}
For our purposes, it is useful to call the saturation of the
effective monoid of a divisor $D$ as the saturation $s$ of the
divisor $D$ on $\sx$. In this case, the saturation $s :=
\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
\geq s$.
\end{rem}

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that minimally generate \todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).  The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

The following lemma provides an inductive method to extend
O'Dorney's result \todo{Aaron: Which result? If anything, wouldn't this be a strengthening of his bounds from Theorem 8, instead of an extension? I guess it is an extension in that it generalizes to higher genus? Cite the theorem number you are talking about} on $\BP^1_k$ to divisors $D = \sum_i \frac{\alpha_i
}{\beta_i} P_i$ consisting of arbitrarily many points satisfying $H^
0(X, \lfloor D \rfloor) > 0$, showing that they \todo{What are generated?} are generated in
degrees at most $e = \max(\beta_i)$ with relations generated in
degrees at most $2e$.  Furthermore, given some constraints on $H^0(
X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
same Riemann-Roch arguments from $\BP^1_k$ in arbitrary genus,
allowing a similar inductive result in arbitrary genus $e = \max(
\beta_i)$. To do this, we extend an inductive result by Voight and
Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
divisors. \todo{cite theorem 8.3.1}

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve with a $\BQ$-divisor $\halfcan'$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0$ for all $x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.  Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then

\begin{enumerate}
\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

\item[(b)] If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then

\begin{align*}
	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n- 1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i + 1} + 1)}: 1\le i =\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}

In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally \todo{Aaron: Should the word minimally be removed here?} generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}

Before presenting a proof of this, we first prove a lemma that will allow parts $(b)$ and $(c)$ to immediately follow from an appropriate construction of generators in part $(a)$. \todo{Would it make sense to put this lemma before the previous theorem, instead of after the statement?}

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.  Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
\begin{enumerate}
\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	& S \\
	\cup \; &\langle T\rangle \\
	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
\end{align*}
\end{enumerate}
Then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose monomial $f\in T$ has a pole order $a$ at $P$.  Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem:sat-1}]
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

\noindent
be the non-negative best lower approximation of $\frac{
\alpha}{\beta}$ as described in the lemma's statement.  Note that elements of $H^0(X, d\halfcan)$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$.  Moreover, a set $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$ \todo{Where do the $z_i$ live? How many $z_i$ are there, what indexing sets are the product and sums taken over?}
by construction, so any product of $\prod z_i$ of elements of
degrees less than $d_i$ must have
\todo{Aaron: at what point is the following order taken at?}
\[
	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
\]

\noindent
so we have the pole order of $\prod z_i$ is 
\[
	\sum -\ord(z_i) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.

Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
\beta}$ not a best lower approximation. Then choose
best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
maximal; since $c<c_{i + 1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$. From
this we can deduce that 
\[
	c_i +(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
\]

\noindent
Therefore, we can generate an element of $(R_{\halfcan})_d$ as a product of lower degrees that 
has pole degree $c$ at $P$ by either $y_i u^b$, $y_i z u^b$, or $zu^b$ satisfying $i>
\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$, 
with $d_j = 1 =d_{{\lfloor \frac{a}{b} \rfloor}}$ and $b<d_{\lfloor \frac{\alpha}{\beta} 
\rfloor + 1}$.

Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
\frac{\alpha}{\beta}$ is not a best lower approximation than we can
construct an element in degree $d$ with pole degree $c$ by either $y
_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
same conditions.  This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.  In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.

@@

We show that $J$ is in fact all of the initial ideal. Suppose
$f$ is a non-constant monomial that does not lie within $J$.
Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
some $x_j \mid f$ or else we would have $y_i x_j \mid f$
contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
element of a relation and divides $f$. If $d_i = 1$ as well, then
we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
f$. We observe that the remaining elements are precisely those of
the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
Therefore, by dimension counting (in each degree), we see that $J$
is the initial ideal of $I$. 
%Furthermore, since our choice of $y_i
%$'s was generic, this is in fact the generic initial ideal.

@@

@@

\begin{lem}
\label{lem:sat-2}
Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.

Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).

Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch). Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}

@@

\begin{align}
\label{eqn:sat_two_add_generator}
		\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
		\geq 0, \epsilon \in \{0, 1\}\} \cup \{ y_3^ay_4 \mid a \geq 0 \}
\end{align}

@@

\todo{transition!}

>>>>

This theorem is proven in three different genus cases, each of
which use similar inductive processes. The high genus case is
proven in Theorem ~\ref{thm:high_generators_relations}. In Theorem
~\ref{thm:g_1_generators_relations} and Theorem
~\ref{thm:g_0_generators_relations}, we also give the respective
genus one and genus zero results after using a similar induction
process while dealing with more complicated base cases and
exceptional cases.

@@

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
\end{enumerate}

@@

\begin{rem}
For our purposes, it is useful to call the saturation of the
effective monoid of a divisor $D$ as the saturation $s$ of the
divisor $D$ on $\sx$. In this case, the saturation $s$ of a divisor
$D$ on $\sx$ (i.e. $\sat(\Eff(D))$) is the smallest positive $s \in
\BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d \geq s$.
\end{rem}

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).

@@

In Lemma \ref{lem:sat-1} we provide an inductive method to strengthen
O'Dorney's result \todo{cite theorem 8} on $\BP^1_k$ to divisors $D = \sum_{i=1}^n \frac{\alpha_i
}{\beta_i} P_i$ for points $P_1, \ldots, P_n$ on a curve $X$ such that $H^
0(X, \lfloor D \rfloor) > 0$; our result implies that $R_D$ is generated in
degrees at most $e = \max(\beta_i)$ with relations generated in
degrees at most $2e$.  Furthermore, given additional constraints on $H^0(
X, \lfloor dD \rfloor)$ for various values of $d$, we can apply the
same Riemann-Roch arguments in arbitrary genus. 
To do this, we extend an inductive result by Voight and
Zureick-Brown on stacky canonical rings to arbitrary $\BQ$-
divisors. \todo{cite theorem 8.3.1}

First, however, we give a criteria to determine if a set of monomials generates the initial ideal of relations, and define notation for a type of monomial ordering.

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.  Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
\begin{enumerate}
\item[(\ref{lem:relations_from_generators_induction}.1)]  $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
\item[(\ref{lem:relations_from_generators_induction}.2)] $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item[(\ref{lem:relations_from_generators_induction}.3)] All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	& S \\
	\cup \; &\langle T\rangle \\
	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
\end{align*}
\end{enumerate}
Then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose monomial $f\in T$ has a pole order $a$ at $P$.  Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ is an element of either $S$, $\langle T\rangle$, or $\initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$,
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{proof}

As suggested by the previous lemma, we will need an ordering on monomials, and the following definition will prove useful in the ensuing lemma.
\begin{defn}
We equip the graded ring $k[x_1, \ldots x_m]$, with weight $a_i$ and pole order $-\ord_P(x_i)$ attached to $x_i$, the graded $P$ reverse lexicographic order {\bf{g-P-revlex}} if for $f=\prod_{i=1}^m {x_i}^{q_i}\ne g=\prod_{i=1}^m {x_i}^{r_i}$, $f\prec g$ iff one of the following holds
\begin{enumerate}
\item $\deg(f) < \deg(g)$
\item $\deg(f) = \deg(g)$ and $-\ord(f) > -\ord(g)$
\item $\deg(f) = \deg(g)$, $-\ord(f) = -\ord(g)$, and for $i$ maximal such that $q_i-r_i$ is non-zero, that expression is negative.  
\end{enumerate}
\end{defn}
We leave it as an exercise to verify that this is an order.  \todo{check for ourselves that this actually is}
We now offer a lemma that allows us to inductively add $\mathbb{Q}$-points to a divisor and describe the new generators and relations.

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve with a $\BQ$-divisor $\halfcan'$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0$ for all $x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.  Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\sigma$ with relations generated
in degree at most $\tau$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then

\begin{enumerate}
\item[(a)] $R_{\halfcan}$ is generated over $R_{\halfcan'}$ by elements $y_1, \ldots, y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$, when viewed as sections of $\so_{\halfcan'}$

\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
\[
	\ord_u(f) < \ord_u(g) \implies f\prec g
\]
and equip $k[y_1, \ldots, y_n]$ with g-P-revlex and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ with a block order.
If $I$ and $I'$ are the ideal of relations of $R_{\halfcan}$ and $R_{\halfcan'}$ respectively, then

\begin{align*}
	\initial_\prec(I) &= \initial_\prec(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle U_i: 1 \le i \le n-1 \rangle\\
										 &+ \langle V \rangle\\
\end{align*}
where 
$V=\{x_i y_j: 1\le i\le m, 1\le j\le n\}$
 and $U_i$ is the set of monomials of the form $\prod_{j=1}^{i} y_i^{a_i}$ with $a_j\in \mathbb{Z}^{\ge 0}, a_i\ne 0$ such that
$\sum_{j=1}^i a_j c_j \ge c_{j+1}$
and there does not exist $((b_1, \ldots b_i)\ne (a_1, \ldots a_i)$ such that with all $b_j\le a_j$ and 
$\sum_{j=1}^i b_jc_j\ge c_{j+1})\}$.  \\

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with relations $I$ generated over $I'$ by relations in degree is generated $\max(2\beta, \beta + \sigma)$ (where $\sigma=\max(\deg(x_i))$).
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}
\begin{proof}
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

\noindent
be the positive best lower approximation of $\frac{
\alpha}{\beta}$ as described in the lemma's statement.  Note that elements of $H^0(X, d\halfcan)$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$.  Moreover, a set $\lfloor d_i \frac{\alpha}{\beta}\rfloor$ elements in $(R_{D})_{d_i}$ with respective pole orders $1, \ldots, \lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent over $(R_{\halfcan'})_d$, and thus by dimension counting form a $k$-basis for
$(R_{\halfcan})_d$ over $(R_{\halfcan'})_d$.

For any $j < i \in \mathbf{N}$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$, so for any $z_1, \ldots, z_n$ with $\deg(z_j)<d_i$ for all $z_j$, $\prod_{j=1}^n z_j$ must satisfy
\[
	\frac{-\ord_P(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
\]

\noindent
so we have the pole order of $\prod_{j=1}^n z_j$ is 
\[
	\sum -\ord(z_j) < c_i .
\]

\noindent
Thus, the elements of $(R_{\halfcan})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees. 
Choose some $y_i \in(R_{
\halfcan})_{d_i}$ with $-\ord_{P}(y_i)=c_i$.  Note that this choice is generic if $d_i>1$ and if $d_i=1$ and $c_i=\lfloor \frac{\alpha}{\beta}\rfloor$.

Suppose $c,d\in \mathbb{N}$ with $d\le \beta$ and $\frac{c}{d} \le \frac{\alpha}{
\beta}$ is not a best lower approximation. Then choose
best lower approximation $\frac{c_i}{d_i}$ with $c_i$ maximal such that $d_i< d$.  This implies $\frac{c_i}{d_i}\ge \frac{c}{d}$ so 
%  The argument goes $c_i d \ge c d_i$
% implies c_i \frac{d}{d_i} \ge c
% implies c_i + \frac{d-d_i}{d_i}c_i \ge c
% \implies c_i (d-d_i) \frac{c_i}{d_i}\ge c
% so since everything is an integer $c_i +\lfloor (d - d_i) \frac{c_i}{d_i}\rfloor \ge c$
% \implies the equation below:
\[
	c_i +\lfloor (d-d_i) \frac{\alpha}{\beta} \rfloor \ge c.
\]

This suggests how we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for $i \in \mathbf{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

Furthermore, if we define $U_i$ and $V$ as in the lemma's statement and
\[
	T = (\bigcup_{i=1}^{n-1} U_i) \cup V,
\]
then we observe that $S$ and $T$ satisfy the hypothesis of Lemma \ref{lem:relations_from_generators_induction}, so we immediately prove part (b) of this lemma.

\iffalse{
Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
\frac{\alpha}{\beta}$ is not a best lower approximation than we can
construct an element in degree $d$ with pole degree $c$ by either $y
_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
same conditions.  This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.  In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.

@@

We show that $J$ is in fact all of the initial ideal. Suppose
$f$ is a non-constant monomial that does not lie within $J$.
Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
some $x_j \mid f$ or else we would have $y_i x_j \mid f$
contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
element of a relation and divides $f$. If $d_i = 1$ as well, then
we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
f$. We observe that the remaining elements are precisely those of
the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
Therefore, by dimension counting (in each degree), we see that $J$
is the initial ideal of $I$. 
}\fi

%Furthermore, since our choice of $y_i
%$'s was generic, this is in fact the generic initial ideal.

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbf{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}

@@

\todo{Something about fractional weight modular forms?}

\begin{lem}
\label{lem:sat-2}
Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log spin curves with coarse space $(X, \Delta, \halfcan_X)$ with signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r- 1}, \delta)$ respectively with $g > 0,$ and, if $g = 1$ then $\deg 3\halfcan' \geq 2$.
Let $R_{L'} = k[x]/I'= k[x_2, x_3
, x_5, \ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X, \lfloor \halfcan'\rfloor) = 0$).
Suppose for $i \in \{2, 3\}$, $\deg x_i = i$ and $\ord_P(x_i)= 0$ (which is satisfied generically in degree 2 and 3, since base-point freeness follows by Riemann-Roch). Choose an ordering on $k[x_2, \ldots, x_m]$ that satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}

@@

\begin{align}
\label{eqn:sat_two_add_generator}
	\begin{split}
		&\{ y_3^ax_2^b x_3^\epsilon \mid a \geq 0, b 
		\geq 0, \epsilon \in \{0, 1\}\} \\
		&\cup \{ y_3^ay_4 \mid a \geq 0 \},
	\end{split}
\end{align}

@@

Transition words.
\todo{transition!}
